### 2019-11-14 manuscript/manuscript.rmd
update phylogenetic signal in manuscript_kernel and mnuascript

Site heterogeneity in equilibrium frequency has been a major concern in tests of Ctenophora-sister and Porifera-sister. This has been addressed with CAT models. iqtree provides a new family of C models that also address site heterogeneity. Given the extensive computational cost and concerns about overparameterization of CAT models, we compared iqtree C results to CAT results for a subset of matrices to see if they give consistent results. This would be of technical interest because it would reduce the cost of accommodating compositional heterogeneity in future analyses. For computational efficiency, we first only applied Poisson+CAT models in every matrice with only Choanoflagellata as outgroup. It should be noted that most Phylobayes runs were converged, several large matrices have not reached convergence after at least a month's computational time.

Interestingly, we found strong supports for both hypotheses when using Poisson-CAT model in Choanimalia matrices. Consistent with previous study, we recovered the strong support of Porifera-sister in matrices of Philippe2008, Ryan2013, and Whelan2015. Moreover, we also found a strong support of Porifera-sister in two Whelan2017 matrices and a weaker support of subsampled matrice of Simion2017. Similar to ML analyses, we found no strong support for either hypothesis in Moroz2013_3d matrice. For the matrices have conflicted results between Poisson-CAT and C models, we further ran Poisson+CAT models with inclusion of more distantly related outgroups to evaluate how outgroup choice will affect phylogenetic inference under CAT model. Consistently with past study, we found strong support of Ctenophora-sister in all anaylzed Opisthokonta matrices, indicating that Ctenophora-sister is also favored in all matrices with more distantly related taxa are used as outgroups.

###

## The current state of understanding

@@

#### Outgroup taxa sampling with C10-C60 and CAT models
Because different choices of outgroups could also affect phylogenetic inference as suggested in previous analyses, we parsed the full data matrices into three different types of outgroups: Choanimalia , Holozoa and Opisthokonta. These datasets include the same set of genes but differ in the composition of outgroup species. Choanimalia only includes choanofagellates as outgroup; Holozoa also includes more distantly related holozoans; Opistokonta also includes Fungi. For each Choanimalia data matrice, both C models IQtree and Poisson-CAT models in PhyloBayes were conducted. The maximum likelihood analysis was performed using the best-fit substitution model identified as above and nodal support was assessed with 1000 ultrafast bootstrap replicates using IQtree. Moreover, bayesian inference with the site-heterogeneous poisson-CAT model was done with PhyloBayes MPI. To minimize computational burden, CAT-GTR models were not in this study.

>>>>

Site heterogeneity in equilibrium frequency has been a major concern in tests of Ctenophora-sister and Porifera-sister. This has been addressed with CAT models. iqtree provides a new family of C models that also address site heterogeneity. Given the extensive computational cost and concerns about overparameterization of CAT models, we compared iqtree C results to CAT results for a subset of matrices to see if they give consistent results. This would be of technical interest because it would reduce the cost of accommodating compositional heterogeneity in future analyses. For computational efficiency, we first only applied Poisson+CAT models in every matrix with only Choanoflagellata as outgroup. It should be noted that most Phylobayes runs were converged, several large matrices have not reached convergence after at least a month's computational time.

Interestingly, we found strong supports for both hypotheses when using Poisson-CAT model in Choanimalia matrices. Consistent with previous study, we recovered the strong support of Porifera-sister in matrices of Philippe2008, Ryan2013, and Whelan2015. Moreover, we also found a strong support of Porifera-sister in two Whelan2017 matrices and a weaker support of subsampled matrix of Simion2017. Similar to ML analyses, we found no strong support for either hypothesis in Moroz2013_3d matrix. For the matrices have conflicted results between Poisson-CAT and C models, we further ran Poisson+CAT models with inclusion of more distantly related outgroups to evaluate how outgroup choice will affect phylogenetic inference under CAT model. Consistently with past study, we found strong support of Ctenophora-sister in all anaylzed Opisthokonta matrices, indicating that Ctenophora-sister is also favored in all matrices with more distantly related taxa are used as outgroups.

### Phylogenetic signal
To further explore the effect of site-homogeneous or site-heterogeneous models and outgroup choices in on the animal-root position,  we next quantify the support of phylogenetic signal over two alternative hypotheses ()
## The current state of understanding

@@

#### Outgroup taxa sampling with C10-C60 and CAT models
Because different choices of outgroups could also affect phylogenetic inference as suggested in previous analyses, we parsed the full data matrices into three different types of outgroups: Choanimalia , Holozoa and Opisthokonta. These datasets include the same set of genes but differ in the composition of outgroup species. Choanimalia only includes choanofagellates as outgroup; Holozoa also includes more distantly related holozoans; Opistokonta also includes Fungi. For each Choanimalia data matrice, both C models IQtree and Poisson-CAT models in PhyloBayes were conducted. The maximum likelihood analysis was performed using the best-fit substitution model identified as above and nodal support was assessed with 1000 ultrafast bootstrap replicates using IQtree. Moreover, bayesian inference with the site-heterogeneous poisson-CAT model was done with PhyloBayes MPI. To minimize computational burden, CAT-GTR models were only performed in the.
